### 2016-02-09 prepReport/stateArt.tex
State of the art chapter completed

\section{Final Overview}\label{sec:overview}

>>>>

\section{Final Overview}\label{sec:overview}
As we could attest from this small literature survey, although there is already an hardware implementation os LSTM, there is still a good deal of room for improvement by adding on chip-learning to the system, and also to restric it to a smaller use of the FPGA resources, allowing it to accomodate a more complex network. Furthermore,~\cite{Tavear13} shows that, at least for that particular case, the LSTM network doesn't suffer a great performance impact from using SPSA training, as opposed to the more common BPTT, and~\cite{Maeda05} showed that an SPSA hardware implementation is feasible. These three conclusions combined indicate that the idea of a hardware LSTM network with on-chip learning using SPSA is possible.

Besides the proposed hardware implementation, it would be advantageous to perform \emph{benchmarks} to see how well it compares with software solutions, and Section~\ref{sec:sa_apps} suggests a handful of examples to test my final solution.
